Effects of Different Pain Relievers and Dosages on Cognitive Retention

### 2025-03-10 paper/paper.qmd
summary stats based on new dataset

# Display table with no row names
kable(summary_table, caption = "Summary Statistics by Time", booktabs = TRUE, row.names = FALSE)

@@

# Display table
kable(drug_summary, caption = "Summary of Drug Types", booktabs = TRUE, row.names = FALSE)

@@

# Display table
kable(dosage_summary, caption = "Summary of Dosage Levels", booktabs = TRUE, row.names = FALSE)

@@

# Display table
kable(age_summary, caption = "Summary of Age Groups", booktabs = TRUE, row.names = FALSE)

>>>>

# Display table with no row names
kable(summary_table, booktabs = TRUE, row.names = FALSE)

@@

# Display table
kable(drug_summary, booktabs = TRUE, row.names = FALSE)

@@

# Display table
kable(dosage_summary, booktabs = TRUE, row.names = FALSE)

@@

# Display table
kable(age_summary, booktabs = TRUE, row.names = FALSE)
